
## Loading and preprocessing the data
1. Read the data
```{r}
dat = read.csv('./activity.csv')
```
2. Transform the data and get the total number of steps per day. There are 8 days
that the records are missing and they are ignored.
```{r}
activity=aggregate(steps~date, dat, sum)
summary(activity$steps)
```

## What is mean total number of steps taken per day?
```{r}
stepsmean = mean(activity$steps, na.rm = T)
stepsmedian = median(activity$steps, na.rm = T)
library(ggplot2)
qplot(activity$steps,binwidth=1000,
      main='histogram of the total number of steps taken each day', 
      xlab='number of steps')
```


So the mean for totol number of steps taken per day is `r format(stepsmean, scientific=FALSE)` and median.
is `r stepsmedian`


## What is the average daily activity pattern?

Transform the data and take avarage steps for each interval
```{r}
interval = aggregate(steps~interval, dat, mean)
```

Creat a plot
```{r}
plot(interval$interval, interval$steps, type = 'l', 
     main="average number of steps during the day", 
     xlab="interval in a day", 
     ylab="Average number of steps")
```


## Imputing missing values

Impute the missing values with the average steps for each interval
```{r}
impute=mean(dat$steps, na.rm = T)
newdat=dat
newdat$steps[is.na(dat$steps)]=impute
activitynew=aggregate(steps~date, newdat, sum)
library(ggplot2)
qplot(activitynew$steps,binwidth=1000,
      main='histogram of the total number of steps taken each day', 
      xlab='number of steps')
newstepsmean = mean(activitynew$steps)
newstepsmedian = median(activitynew$steps)

```
So the mean for totol number of steps taken per day after imputing 
is `r format(newstepsmean, scientific=FALSE)` compared to `r format(newstepsmean, scientific=FALSE)` without imputing and the median is `r format(newstepsmedian,
scientific=FALSE)` 
vs `r stepsmedian`. They are the same except for the median as I used mean to impute.


## Are there differences in activity patterns between weekdays and weekends?


Create a new column to assign the day('Monday', 'Tuesday',...) in a week and 
creat another column to assgn 'weekday' or 'weekend'
```{r}
newdat$week=weekdays(as.Date(newdat$date,"%Y-%m-%d"))
newdat$weektype=ifelse(newdat$week=='Sunday'|newdat$week=='Saturday',
                            'Weekend','Weekday')
activityweekend=aggregate(steps~interval+weektype, newdat, mean)
qplot(interval, steps, data = activityweekend, geom = 'line' , facets = 
              weektype~., color=weektype)
```
